\documentclass[12pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{longtable}

\pagestyle{fancy}
\fancyhf{}
\rhead{\thepage}
\lhead{OghmaNotes -- SRS}

\title{Software Requirements Specification \\
\Large OghmaNotes: RAG-Powered Learning Platform}
\author{Samuel Regan, Semyon Fox, Shreyansh Singh}
\date{\today}

\hypersetup{
    pdftitle={OghmaNotes SRS},
    pdfauthor={Samuel Regan, Semyon Fox, Shreyansh Singh}
}

\begin{document}

\maketitle

\tableofcontents
\newpage

%==============================================================================
\section{Introduction}
%==============================================================================

\subsection{Purpose}

This Software Requirements Specification (SRS) defines the functional and non-functional requirements for \textbf{OghmaNotes}, an AI-powered study platform that combines portable Markdown notes with Retrieval-Augmented Generation (RAG) to provide intelligent learning from course materials.

The document establishes a shared contract between the development team and academic stakeholders. The SRS focuses on \emph{what} the system shall do and the quality attributes it shall meet.

\textit{Intended Audience:} Development team, academic stakeholders, maintainers, and QA engineers.

\subsection{Key Stakeholders}

\begin{enumerate}
    \item \textbf{Development Team}: Three developers working in parallel across frontend, backend, and database infrastructure.
    \item \textbf{Academic Stakeholder}: Approves scope and evaluates deliverables.
    \item \textbf{End Users}: University students (primary).
\end{enumerate}

\subsection{Scope and Objectives}

\subsubsection{System Scope}

OghmaNotes is a web-based learning platform allowing students to:

\begin{itemize}
    \item Create and manage Markdown notes with offline-first support (PWA).
    \item Ingest and index PDFs into a vector database for semantic retrieval.
    \item Ask questions about materials through RAG-powered chat with citations.
    \item Generate adaptive quizzes and spaced-repetition flashcards.
    \item Track progress with an analytics dashboard.
    \item Integrate with LMS platforms (Canvas) to sync deadlines.
\end{itemize}

\subsubsection{In Scope}

\begin{itemize}
    \item Web-based Markdown note editor with offline support (PWA).
    \item PDF ingestion, text extraction, semantic chunking, and vector storage.
    \item LMS integration (Canvas) for assignment and deadline sync.
    \item RAG chat with cited answers.
    \item Adaptive quiz generation.
    \item Spaced repetition (SM-2) flashcards.
    \item Calendar and timetable for tasks and study sessions.
    \item Analytics dashboard with progress tracking.
    \item Full vault export (notes, metadata, settings).
    \item Bidirectional note linking and knowledge graph visualization.
    \item Flexible tagging system.
    \item Multi-mode search (keyword, semantic, hybrid).
    \item User authentication with email verification and password reset.
    \item User profile management.
    \item Responsive design for desktop and tablet.
\end{itemize}

\subsubsection{Out of Scope}

\begin{itemize}
    \item Real-time collaborative multi-user editing.
    \item Video/audio transcription.
    \item Native mobile apps (PWA only).
    \item Instructor dashboards.
    \item Light mode (dark only).
    \item WCAG full compliance.
\end{itemize}

\subsubsection{Key Objectives}

\begin{enumerate}
    \item Deliver feature-complete product by end of semester.
    \item Enable 3-person parallel development via clear API contracts.
    \item Auto-deploy from production branch.
    \item Stay within budget constraints.
\end{enumerate}

\subsection{References}

\begin{itemize}
    \item \textbf{Notea} (\url{https://github.com/QingWei-Li/notea}) -- MIT License. Used as scaffold for note-taking interface.
    \item PostgreSQL Vector Documentation: \url{https://github.com/pgvector/pgvector}
    \item OpenAPI 3.1 Specification for REST API contracts.
\end{itemize}

\subsection{About the Name}

\textbf{Oghma} (pronounced ``OH-muh'') is the Celtic deity of eloquence, learning, and writing. He created Ogham, the ancient Irish writing system, to preserve and share knowledge. This platform embodies the same mission: structured learning systems that help students organize and retrieve knowledge effectively.

%==============================================================================
\section{Overall Description}
%==============================================================================

\subsection{Product Perspective}

OghmaNotes is a new web-based Progressive Web App deployed on AWS. It integrates with external services (Canvas, OpenAI API, S3 storage) and uses PostgreSQL with pgvector for relational and vector search.

Architecture:
\begin{itemize}
    \item \textbf{Frontend}: Next.js PWA with React and Tailwind CSS.
    \item \textbf{Backend}: Next.js API routes in a single monolith.
    \item \textbf{Database}: PostgreSQL 12+ with pgvector extension.
    \item \textbf{Storage}: AWS S3 for PDFs and exports.
    \item \textbf{Background Jobs}: Synchronous initially; async via deferred jobs if needed.
\end{itemize}

\subsection{Product Functions}

\begin{itemize}
    \item Manage user accounts with email verification and password reset.
    \item Create, edit, organize, and sync Markdown notes.
    \item Ingest and index PDFs for semantic retrieval.
    \item Provide RAG-based chat with cited answers.
    \item Generate and manage quizzes.
    \item Manage flashcards with spaced-repetition scheduling.
    \item Integrate LMS deadlines into a unified calendar.
    \item Provide analytics on study progress.
    \item Export entire vault as downloadable archive.
    \item Link notes and visualize knowledge graphs.
    \item Tag and organize notes.
    \item Search using keyword, semantic, or hybrid modes.
\end{itemize}

\subsection{User Characteristics}

\begin{itemize}
    \item \textbf{Primary Users}: Undergraduate and postgraduate students.
    \item \textbf{Technical Proficiency}: Basic digital literacy; no programming required.
    \item \textbf{Accessibility}: Keyboard navigation and dark mode support.
\end{itemize}

\subsection{Constraints}

\begin{itemize}
    \item \textbf{Tech Stack}: Next.js, PostgreSQL with pgvector, AWS S3, OpenAI API, Docker.
    \item \textbf{Deployment}: AWS Amplify auto-deploy from production branch.
    \item \textbf{Storage}: 5GB per user quota.
    \item \textbf{Timeline}: End of semester delivery.
    \item \textbf{Team}: 3 developers, ~few hours per day.
\end{itemize}

\subsection{Assumptions}

\begin{itemize}
    \item OpenAI API available; user provides own API keys.
    \item S3 and PostgreSQL instances are provisioned.
    \item Canvas LMS API accessible for read-only sync.
    \item Users have modern browsers (Chrome 90+, Firefox 88+, Safari 14+, Edge 90+).
    \item Stable internet for sync; offline usage limited to PWA notes.
\end{itemize}

%==============================================================================
\section{Functional Requirements}
%==============================================================================

\subsection{Feature Priority}

\begin{table}[h]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Priority} & \textbf{Description} \\
\midrule
\textbf{Must Have} & Core features required for MVP \\
\textbf{Should Have} & Important enhancements \\
\textbf{Nice to Have} & Polish and advanced features \\
\bottomrule
\end{tabular}
\end{table}

\subsection{User Stories and Requirements}

\subsubsection{Story 1: Authentication and Account Management}

\textbf{As a} student, \textbf{I want to} register, verify my email, log in, and manage my account, \textbf{so that} my data is secure and I can recover access.

\paragraph{Requirements}

\begin{itemize}
    \item \textbf{FR-1.1} Register with email and password; email verification required.
    \item \textbf{FR-1.2} Login with JWT tokens (24h expiry).
    \item \textbf{FR-1.3} Password reset via email link (1h token, single-use).
    \item \textbf{FR-1.4} Logout to invalidate session.
    \item \textbf{FR-1.5} Passwords stored as bcrypt hashes (10+ rounds).
    \item \textbf{FR-1.6} Update email and password from settings.
    \item \textbf{FR-1.7} Delete account with 7-day soft-delete period.
\end{itemize}

Priority: \textbf{Must Have}

\subsubsection{Story 2: Create and Manage Markdown Notes}

\textbf{As a} student, \textbf{I want to} create, edit, and organize notes in Markdown, \textbf{so that} I can structure course materials portably.

\paragraph{Requirements}

\begin{itemize}
    \item \textbf{FR-2.1} Split-pane editor with live Markdown preview.
    \item \textbf{FR-2.2} Support Markdown syntax (headers, lists, code, tables, LaTeX math).
    \item \textbf{FR-2.3} Auto-save to IndexedDB every 5 seconds.
    \item \textbf{FR-2.4} Organize notes into folder hierarchy.
    \item \textbf{FR-2.5} Sync to S3 when online; resolve conflicts with last-write-wins.
    \item \textbf{FR-2.6} Offline editing with auto-sync on reconnect.
\end{itemize}

Priority: \textbf{Must Have}

\subsubsection{Story 3: PDF Upload and Indexing}

\textbf{As a} student, \textbf{I want to} upload PDFs and have them indexed for search and RAG, \textbf{so that} I can query course materials.

\paragraph{Requirements}

\begin{itemize}
    \item \textbf{FR-3.1} Upload PDFs up to 50 MB (within 5GB quota).
    \item \textbf{FR-3.2} Extract text from PDFs.
    \item \textbf{FR-3.3} Split text into semantic chunks (500 tokens, 50--100 token overlap).
    \item \textbf{FR-3.4} Generate embeddings (OpenAI text-embedding-3-small, 1536 dims) and store in PostgreSQL pgvector.
    \item \textbf{FR-3.5} Preserve page numbers and section metadata in chunks.
    \item \textbf{FR-3.6} Display ingestion progress.
    \item \textbf{FR-3.7} Handle errors gracefully (rate limits, API unavailable).
\end{itemize}

Priority: \textbf{Must Have}

\subsubsection{Story 4: Multi-Mode Search}

\textbf{As a} student, \textbf{I want to} search my notes and PDFs by keyword or meaning, \textbf{so that} I can find information even without exact terms.

\paragraph{Requirements}

\begin{itemize}
    \item \textbf{FR-4.1} Keyword search using PostgreSQL FULLTEXT (~5ms).
    \item \textbf{FR-4.2} Semantic search using pgvector embeddings (~50ms).
    \item \textbf{FR-4.3} Hybrid search combining both modes (~100ms).
    \item \textbf{FR-4.4} Filter results by tags, module, document type, semester.
    \item \textbf{FR-4.5} Display results with relevance scores and snippets.
    \item \textbf{FR-4.6} Cmd+K overlay for keyboard-first search.
\end{itemize}

Priority: \textbf{Must Have}

\subsubsection{Story 5: RAG Chat with Citations}

\textbf{As a} student, \textbf{I want to} ask questions about my materials and receive answers with source citations, \textbf{so that} I can verify answers and reference specific pages.

\paragraph{Requirements}

\begin{itemize}
    \item \textbf{FR-5.1} Chat interface for free-text questions.
    \item \textbf{FR-5.2} Perform hybrid search to retrieve top 5 relevant chunks.
    \item \textbf{FR-5.3} Send chunk text and query to LLM for answer generation.
    \item \textbf{FR-5.4} Include citations (page number, section, chunk ID) in responses.
    \item \textbf{FR-5.5} Render citations as clickable links to PDF location.
    \item \textbf{FR-5.6} Stream LLM response token-by-token.
    \item \textbf{FR-5.7} Allow users to rate responses.
    \item \textbf{FR-5.8} Handle LLM unavailability gracefully.
\end{itemize}

Priority: \textbf{Must Have}

\subsubsection{Story 6: Quiz Generation}

\textbf{As a} student, \textbf{I want to} generate practice quizzes from my notes and PDFs, \textbf{so that} I can test understanding and identify weak areas.

\paragraph{Requirements}

\begin{itemize}
    \item \textbf{FR-6.1} Select note or document section and choose difficulty.
    \item \textbf{FR-6.2} Generate 5--10 questions from selected content.
    \item \textbf{FR-6.3} Support multiple-choice, short-answer, and true/false types.
    \item \textbf{FR-6.4} Optional timed mode with per-question countdown.
    \item \textbf{FR-6.5} Display total score and correct answers after completion.
    \item \textbf{FR-6.6} Tag and track weak topics based on performance.
\end{itemize}

Priority: \textbf{Must Have}

\subsubsection{Story 7: Spaced Repetition Flashcards}

\textbf{As a} student, \textbf{I want to} use SM-2 flashcards for efficient review, \textbf{so that} I can master material through optimal spacing.

\paragraph{Requirements}

\begin{itemize}
    \item \textbf{FR-7.1} Create flashcard decks from notes or quiz content.
    \item \textbf{FR-7.2} Display daily review queue (``Due Today: N cards'').
    \item \textbf{FR-7.3} Flip cards and rate recall on 1--5 scale.
    \item \textbf{FR-7.4} Update SM-2 interval and ease factor based on ratings.
    \item \textbf{FR-7.5} Persist flashcard state across devices.
    \item \textbf{FR-7.6} Display progress metrics (due, reviewed, mastery \%).
\end{itemize}

Priority: \textbf{Must Have}

\subsubsection{Story 8: Canvas LMS Integration}

\textbf{As a} student with Canvas courses, \textbf{I want to} sync assignments and deadlines, \textbf{so that} I can plan study around course requirements.

\paragraph{Requirements}

\begin{itemize}
    \item \textbf{FR-8.1} Connect Canvas account via OAuth.
    \item \textbf{FR-8.2} Import assignments and exams with due dates.
    \item \textbf{FR-8.3} Display assignments in calendar view.
    \item \textbf{FR-8.4} Auto-schedule study sessions before exams.
    \item \textbf{FR-8.5} Auto-sync once per day; on-demand sync button available.
    \item \textbf{FR-8.6} Handle sync errors gracefully.
\end{itemize}

Priority: \textbf{Should Have}

\subsubsection{Story 9: Study Calendar and Timetable}

\textbf{As a} student, \textbf{I want to} view study schedule and deadlines in a unified calendar, \textbf{so that} I can manage time effectively.

\paragraph{Requirements}

\begin{itemize}
    \item \textbf{FR-9.1} Week and month calendar views.
    \item \textbf{FR-9.2} Display flashcard reviews, quizzes, and LMS assignments.
    \item \textbf{FR-9.3} Auto-schedule reviews before exams.
    \item \textbf{FR-9.4} Click events to navigate to associated task.
    \item \textbf{FR-9.5} Export calendar to iCal format.
\end{itemize}

Priority: \textbf{Should Have}

\subsubsection{Story 10: Analytics Dashboard}

\textbf{As a} student, \textbf{I want to} see my study progress and weak topics, \textbf{so that} I can focus review on areas needing work.

\paragraph{Requirements}

\begin{itemize}
    \item \textbf{FR-10.1} Display study time by period (weekly/monthly).
    \item \textbf{FR-10.2} Display quiz scores over time.
    \item \textbf{FR-10.3} Identify and rank weak topics.
    \item \textbf{FR-10.4} Provide charts for performance and mastery progression.
\end{itemize}

Priority: \textbf{Should Have}

\subsubsection{Story 11: Vault Export}

\textbf{As a} student, \textbf{I want to} export my entire vault, \textbf{so that} I have a portable backup and can migrate to other tools.

\paragraph{Requirements}

\begin{itemize}
    \item \textbf{FR-11.1} Export all notes, metadata, and settings as ZIP archive.
    \item \textbf{FR-11.2} Include notes in Markdown with folder structure preserved.
    \item \textbf{FR-11.3} Include flashcard state and quiz history as JSON.
    \item \textbf{FR-11.4} Embed timestamp and user ID in archive.
\end{itemize}

Priority: \textbf{Should Have}

\subsubsection{Story 12: Note Tagging and Linking}

\textbf{As a} student, \textbf{I want to} tag notes and create bidirectional links, \textbf{so that} I can build a connected knowledge base.

\paragraph{Requirements}

\begin{itemize}
    \item \textbf{FR-12.1} Add arbitrary tags to notes.
    \item \textbf{FR-12.2} Create bidirectional links using wiki-style syntax (\texttt{[[Note Title]]}).
    \item \textbf{FR-12.3} Display backlinks in note view.
    \item \textbf{FR-12.4} Visualize knowledge graph of connections.
    \item \textbf{FR-12.5} Filter notes by tags.
\end{itemize}

Priority: \textbf{Should Have}

\subsubsection{Story 13: Share Materials with Study Groups}

\textbf{As a} student, \textbf{I want to} share note collections with classmates, \textbf{so that} study groups can collaborate.

\paragraph{Requirements}

\begin{itemize}
    \item \textbf{FR-13.1} Generate shareable read-only links for note folders.
    \item \textbf{FR-13.2} Include original author attribution.
    \item \textbf{FR-13.3} Allow recipients to copy shared materials.
    \item \textbf{FR-13.4} Allow authors to revoke access.
\end{itemize}

Priority: \textbf{Nice to Have}

\subsubsection{Story 14: Individual Note Export}

\textbf{As a} student, \textbf{I want to} export individual notes to PDF and analytics to CSV, \textbf{so that} I can share or archive specific materials.

\paragraph{Requirements}

\begin{itemize}
    \item \textbf{FR-14.1} Export single note or folder to PDF.
    \item \textbf{FR-14.2} Preserve Markdown formatting in PDF.
    \item \textbf{FR-14.3} Include table of contents for multi-note exports.
    \item \textbf{FR-14.4} Export analytics data as CSV.
\end{itemize}

Priority: \textbf{Nice to Have}

%==============================================================================
\section{Non-Functional Requirements}
%==============================================================================

\subsection{Performance}

\begin{itemize}
    \item \textbf{NFR-P-1} RAG query end-to-end: $\leq 3$ seconds.
    \item \textbf{NFR-P-2} PDF indexing (50MB): $\leq 2$ minutes.
    \item \textbf{NFR-P-3} Keyword search: $\leq 5$ ms; semantic search: $\leq 50$ ms; hybrid: $\leq 100$ ms.
    \item \textbf{NFR-P-4} Quiz generation: $\leq 5$ seconds.
    \item \textbf{NFR-P-5} Note sync (500KB): $\leq 2$ seconds.
    \item \textbf{NFR-P-6} Cold page load: $\leq 4$ seconds; cached: $\leq 2$ seconds.
    \item \textbf{NFR-P-7} Backend handles 10+ concurrent requests without degradation.
\end{itemize}

\subsection{Security}

\begin{itemize}
    \item \textbf{NFR-S-1} APIs require valid JWT (except login, register, verify).
    \item \textbf{NFR-S-2} Passwords hashed with bcrypt (salt $\geq 10$).
    \item \textbf{NFR-S-3} All communications use TLS 1.2+.
    \item \textbf{NFR-S-4} CORS restricts approved origins.
    \item \textbf{NFR-S-5} Rate limiting on public endpoints.
    \item \textbf{NFR-S-6} Credentials and keys in environment variables, encrypted at rest.
    \item \textbf{NFR-S-7} S3 presigned URLs expire in 1 hour.
    \item \textbf{NFR-S-8} Vector searches filtered by user ID.
    \item \textbf{NFR-S-9} Password reset tokens expire 1 hour, single-use.
    \item \textbf{NFR-S-10} Email verification tokens expire 24 hours.
\end{itemize}

\subsection{Reliability}

\begin{itemize}
    \item \textbf{NFR-R-1} 99\% availability during grading window.
    \item \textbf{NFR-R-2} Automated database backups (AWS RDS).
    \item \textbf{NFR-R-3} Failed jobs retry up to 3 times with exponential backoff.
    \item \textbf{NFR-R-4} Graceful error handling for external API failures.
    \item \textbf{NFR-R-5} User sessions survive service restarts.
    \item \textbf{NFR-R-6} PWA reconnects within 30 seconds of network loss.
\end{itemize}

\subsection{Usability}

\begin{itemize}
    \item \textbf{NFR-U-1} Modern, clean design (Material Design 3 or similar).
    \item \textbf{NFR-U-2} New user completes register $\to$ upload PDF $\to$ ask question in $\leq 5$ minutes.
    \item \textbf{NFR-U-3} Real-time form validation with password strength indicators.
    \item \textbf{NFR-U-4} Keyboard navigation support.
    \item \textbf{NFR-U-5} Responsive layout (desktop, tablet).
    \item \textbf{NFR-U-6} Actionable, non-technical error messages.
    \item \textbf{NFR-U-7} Dark mode only (default).
\end{itemize}

\subsection{Maintainability}

\begin{itemize}
    \item \textbf{NFR-M-1} JavaScript/TypeScript complies with ESLint and Prettier.
    \item \textbf{NFR-M-2} APIs documented using OpenAPI 3.1.
    \item \textbf{NFR-M-3} Database changes via version-controlled migrations.
    \item \textbf{NFR-M-4} Structured JSON logging.
    \item \textbf{NFR-M-5} README describes setup and deployment.
    \item \textbf{NFR-M-6} Automated dependency scanning (Dependabot).
\end{itemize}

%==============================================================================
\section{External Interface Requirements}
%==============================================================================

\subsection{User Interfaces}

\subsubsection{Authentication}
\begin{itemize}
    \item Registration: Email, password, university, degree, graduation year.
    \item Login: Email, password, "Forgot password?" link.
    \item Email verification and password reset flows.
\end{itemize}

\subsubsection{Settings}
\begin{itemize}
    \item Profile: Update email (with re-verification), change password, course info.
    \item Preferences: Language, theme (dark only).
    \item Account: Storage display, delete with confirmation.
\end{itemize}

\subsubsection{Editor}
\begin{itemize}
    \item Split-pane Markdown editor with live preview.
    \item Left sidebar: Folder/note tree.
    \item Top navigation: Upload PDF, RAG Chat, Quiz, Flashcards, Analytics, Settings.
    \item Status bar: Offline indicator, sync progress, storage usage.
    \item Command palette: Cmd+K/Ctrl+K.
\end{itemize}

\subsubsection{RAG Chat}
\begin{itemize}
    \item Message history with timestamps.
    \item Input: ``Ask a question about your materials...''
    \item Response: Formatted text with clickable citations.
    \item Feedback: Thumbs up/down buttons.
\end{itemize}

\subsubsection{Quiz}
\begin{itemize}
    \item One question per screen.
    \item Progress bar and question counter.
    \item Multiple-choice or short-answer input.
    \item Optional timer for timed mode.
    \item Results: Score, breakdown, weak topics.
\end{itemize}

\subsubsection{Flashcards}
\begin{itemize}
    \item Card display with front/back and flip animation.
    \item Response buttons: 1--5 scale (Forget to Perfect).
    \item Progress indicators: Due today, reviewed today.
\end{itemize}

\subsubsection{Calendar}
\begin{itemize}
    \item Week/month views.
    \item Color-coded events: Reviews (blue), LMS (red), study (green).
    \item Click to open details or start task.
    \item Manual sync button for LMS updates.
\end{itemize}

\subsection{Database Interface}

\subsubsection{Storage Architecture}

\begin{itemize}
    \item \textbf{PostgreSQL}: Metadata, searchable content, embeddings, relational data.
    \item \textbf{S3-Compatible Storage}: Full Markdown files and uploaded PDFs.
\end{itemize}

\subsubsection{Data Entities}

\begin{itemize}
    \item User accounts with auth credentials, profile, course info, quotas.
    \item Notes with folder organization, metadata, searchable text.
    \item Vector embeddings for semantic retrieval with metadata (page, section).
    \item PDFs with file metadata, S3 paths, indexing status.
    \item Quizzes and flashcards with SM-2 parameters.
    \item Calendar events and LMS assignments.
    \item Sharing permissions and access control.
    \item Authentication tokens (password reset, email verification).
    \item Analytics data (study time, quiz scores, weak topics).
\end{itemize}

\subsubsection{Database Capabilities}

\begin{itemize}
    \item \textbf{FULLTEXT Search}: Fast keyword search (~5ms).
    \item \textbf{Vector Similarity}: pgvector-based nearest neighbor search (~50ms).
    \item \textbf{Hybrid Search}: Combined keyword and semantic (<100ms).
    \item \textbf{User-Scoped Queries}: All queries filtered by user ID.
    \item \textbf{Filtering and Faceting}: By tags, module, document type, year, semester.
    \item \textbf{ACID Compliance}: For critical workflows.
    \item \textbf{Schema Migrations}: Version-controlled changes.
\end{itemize}

\subsection{External Services}

\begin{itemize}
    \item \textbf{OpenAI API}: Embeddings (text-embedding-3-small, 1536 dims) and chat completion.
    \item \textbf{S3-Compatible Storage}: For notes, PDFs, exports.
    \item \textbf{PostgreSQL}: Relational and vector database.
    \item \textbf{Canvas LMS API}: OAuth and assignment sync (read-only).
    \item \textbf{AWS SES}: Transactional emails.
    \item \textbf{JWT}: Session authentication (no external SSO required).
\end{itemize}

%==============================================================================
\section{Data and Legal Requirements}
%==============================================================================

\subsection{Data Handling}

\begin{itemize}
    \item Data at rest encrypted (S3 server-side, PostgreSQL encryption).
    \item Data in transit encrypted (TLS 1.2+).
    \item User data retained until account deletion; 7-day soft-delete before hard delete.
    \item Users can export all notes and metadata.
    \item Account deletion removes notes, embeddings, quiz history within 7 days.
    \item Password reset and email tokens hashed before storage.
\end{itemize}

\subsection{Compliance}

\begin{itemize}
    \item \textbf{GDPR}: Data subject rights (access, deletion, portability) within project scope.
    \item \textbf{Notea Attribution}: MIT License compliance in documentation and UI.
    \item \textbf{Copyright}: Users responsible for uploaded content; system tracks attribution for shares.
\end{itemize}

\subsection{Audit and Logging}

\begin{itemize}
    \item API access logs: Timestamp, user ID, endpoint, status code.
    \item Document upload logs: File size, hash, user, timestamp.
    \item Authentication events: Login, logout, password reset, email verify.
    \item Deletion logs: Timestamp, user, content hash for recovery.
    \item Retention: 90+ days.
\end{itemize}

%==============================================================================
\section{Verification and Acceptance}
%==============================================================================

\subsection{Testing Strategy}

\begin{itemize}
    \item \textbf{Unit Tests}: Core logic with 70\%+ coverage.
    \item \textbf{Integration Tests}: API endpoints with test database.
    \item \textbf{E2E Tests}: Critical user flows.
    \item \textbf{Manual QA}: Realistic usage scenarios.
    \item \textbf{Performance}: Lighthouse audits for frontend.
\end{itemize}

\subsection{Acceptance Criteria}

System is acceptable when:

\begin{enumerate}
    \item All Must Have requirements are implemented and verified.
    \item Non-functional requirements met for representative workloads.
    \item \texttt{docker compose up} works from scratch.
    \item E2E workflow: register $\to$ verify $\to$ upload PDF $\to$ ask RAG question $\to$ generate quiz $\to$ review flashcard.
    \item AWS Amplify auto-deploy from production branch works.
    \item Code coverage $\geq 70\%$ for core logic.
    \item Academic stakeholder approval.
\end{enumerate}

\subsection{Deployment}

\begin{itemize}
    \item \textbf{Local}: \texttt{docker compose up} starts all services.
    \item \textbf{CI}: Automated tests, linting, OpenAPI validation on push.
    \item \textbf{Production}: AWS Amplify auto-deploys from production branch.
    \item \textbf{Branch Strategy}: Feature branches $\to$ dev (review) $\to$ production (auto-deploy).
\end{itemize}

%==============================================================================
\section*{Appendix A: Glossary}
%==============================================================================

\begin{itemize}
    \item \textbf{RAG}: Retrieval-Augmented Generation. Vector embeddings retrieve relevant text chunks; LLM generates grounded, cited answers.
    \item \textbf{PWA}: Progressive Web App. Installable web app with offline support.
    \item \textbf{SM-2}: SuperMemo 2 spaced repetition algorithm.
    \item \textbf{JWT}: JSON Web Token for secure authentication.
    \item \textbf{Vector Embedding}: Numerical representation (1536-dim) for semantic similarity search.
    \item \textbf{Chunking}: Splitting documents into segments (500 tokens, 50--100 overlap) for embedding.
    \item \textbf{pgvector}: PostgreSQL extension for vector similarity search.
    \item \textbf{FULLTEXT}: PostgreSQL full-text search for keyword matching.
    \item \textbf{Bidirectional Links}: Wiki-style connections between notes.
    \item \textbf{AWS SES}: Simple Email Service for transactional emails.
\end{itemize}

%==============================================================================
\section*{Appendix B: Use Cases}
%==============================================================================

\subsection*{Use Case 1: First-Time User Onboarding}

\textbf{Actor}: New student user

\textbf{Flow}:
\begin{enumerate}
    \item User navigates and clicks ``Sign Up''.
    \item Enters email, password, university, degree, graduation year.
    \item System sends verification email.
    \item User verifies email and gains full access.
    \item User uploads a lecture PDF.
    \item System extracts text, creates 500-token chunks, generates embeddings, stores in PostgreSQL.
    \item User asks: ``What are the key topics in this lecture?''
    \item System performs hybrid search, retrieves chunks, sends to LLM with context.
    \item LLM streams response with citations to page numbers.
\end{enumerate}

\subsection*{Use Case 2: Password Reset}

\textbf{Actor}: User who forgot password

\textbf{Flow}:
\begin{enumerate}
    \item User clicks ``Forgot Password?''
    \item Enters email; system sends reset link (1h token).
    \item User clicks link and enters new password.
    \item System updates hash and invalidates token.
    \item User logs in with new password.
\end{enumerate}

\subsection*{Use Case 3: Daily Review Routine}

\textbf{Actor}: Returning student

\textbf{Flow}:
\begin{enumerate}
    \item User opens app; dashboard shows ``Due Today: 12 flashcards, 1 quiz.''
    \item User reviews flashcards, rating each 1--5.
    \item System updates SM-2 intervals.
    \item User takes generated quiz and views score.
    \item System updates analytics dashboard.
\end{enumerate}

\subsection*{Use Case 4: LMS Sync and Manual Refresh}

\textbf{Actor}: Student with Canvas account

\textbf{Flow}:
\begin{enumerate}
    \item System auto-syncs Canvas assignments daily.
    \item User opens calendar and sees LMS assignments.
    \item New assignment posted; user clicks ``Sync Now''.
    \item System triggers on-demand sync.
    \item Calendar updates with new assignment or shows error message.
\end{enumerate}

\subsection*{Use Case 5: Building Knowledge Graph}

\textbf{Actor}: Student organizing materials

\textbf{Flow}:
\begin{enumerate}
    \item User creates note on "Binary Search Trees"; adds tags: "algorithms", "exam-prep".
    \item User links to another note: \texttt{[[Sorting Algorithms]]}.
    \item System creates bidirectional link.
    \item User clicks ``View Graph'' to see visualization.
    \item User navigates through connected notes.
\end{enumerate}

\end{document}
